My title

### 2024-01-22 outputs/paper/paper.qmd
finish data part and finish paper.qmd draft

```{r}
#| include: false
#| warning: false
#| message: false
install.packages("opendatatoronto")
library("janitor")
library("knitr")
library("lubridate")
library("opendatatoronto")
library("tidyverse")
library(palmerpenguins)
```

@@

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

@@

plot(first_model, "rhat")
```

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
library("janitor")
library("knitr")
library("lubridate")
library("opendatatoronto")
library("tidyverse")
```

@@

# Data {#sec-data}
col.names = c("Year of Death", "Cause of Death", "Age Group", "Gender", "Count", "Cause Group"),
Some of our data is of penguins (@fig-bills), from @palmerpenguins.
```{r}
#| warning: false
#| message: false

file_path <- "../../inputs/data/raw_data.csv"
toronto_homeless_death <- read.csv(file_path)
sample_data <- head(toronto_homeless_death, 6)
table_output <- kable(sample_data,

                      caption = "Sample Table for Causes of Death")
# Print the table
cat(table_output)
```

```{r}
#| label: fig-causes-of-death
#| fig-cap: Causes of death analysis
#| echo: false

ggplot(data = toronto_homeless_death,mapping =  aes(x = Cause_of_death, fill = Age_group)) +
  geom_bar(position = "stack") +
  scale_fill_manual(values = c("lightblue", "lightgreen", "lightpink", "lightyellow", "lightgray")) +
  labs(title = "Causes of Death Stacked by Age Group",
       x = "Cause of Death",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")

```{r}

```

@@

Our results are summarized in @tbl-modelresults.
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```{r}

```
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```{r}

```

@@

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

@@

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```{r}

```

@@

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

@@

plot(first_model, "rhat")
```{r}

```
